Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-09-05 paper/pool_model.tex
exit before finishing Conclusion

>>>>

We introduced the pool model as a novel framework to unify existing approaches and allows researchers to follow a mechanistic approach during model development.
It is able to capture the effects of many established models and provides a lens which is useful to generalize existing systems and results in better overall explainability.

\textbf{CHRISTIAN HELP!}
